\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{8pt}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
	\textbf{\Huge Kevin Montoya Campaña} \\ \vspace{1pt}
	\small \href{https://www.kmontocam.com}{\underline{Portfolio}} $|$ \href{mailto:me@kmontocam.com}{\underline{me@kmontocam.com}} $|$
	\href{https://linkedin.com/in/kmontocam}{\underline{linkedin.com/in/kmontocam}} $|$
	\href{https://github.com/kmontocam}{\underline{github.com/kmontocam}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Tecnológico de Monterrey}{Monterrey, MX}
{B.S in Data Science and Mathematics Engineering - GPA: 97/100}
{Aug. 2020 - Jun. 2024}
\resumeItemListStart
\resumeItem{Courses Overview: Machine Learning, Deep Learning, Cryptography, Statistical Analysis, Data Analysis}
\resumeItem{\textbf{Cybersecurity Specialization}. DevSecOps, Social Engineering, Role-based Access Control}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Machine Learning Engineer II}
{Aug 2023 -- Present} {Hey, Inc}{Monterrey, MX}
\resumeItemListStart
\resumeItem{Deployed multiple \textbf{Kubernetes} clusters to manage all projects within the Artificial Intelligence Department using Azure Kubernetes Services. Configured Ingress Controllers, Observability and Telemetry solutions, Showback mechanisms and autoscaling to enhance scalability and ensure production readiness.}
\resumeItem{Implementation of self-hosted text embedding and Large Language Models (LLMs) from \textbf{Hugging Face}, alongside vector stores using \textbf{Milvus}. These components are seamlessly integrated within containerized platforms, resulting in a cost and response time reduction by 50\%.}
\resumeItem{Administering a complete \textbf{Azure} Subscription via Infrastructure as Code, employing \textbf{Terraform} and \textbf{Terragrunt} for parameterization and environment segregation.}
\resumeItem{Managed Open Source Continuous Integration tools, using \textbf{Jenkins} and GitOps solutions like \textbf{ArgoCD} to automate workflows and significantly enhance team productivity.}
\resumeItemListEnd
\resumeSubheading
{Project Processes and IT Participant Digital Enablement}
{February 2023 -- June 2023}{CEMEX S.A.B. de C.V.}{Prague, CZ}
\resumeItemListStart
\resumeItem{Implementation a Factory Design Pattern to create connections with multiple Database Systems. Using abstract classes in a modular design with \textbf{Python}.}
\resumeItem{Containerization of a machine learning application, seamlessly integrating \textbf{Docker} and \textbf{Tensorflow} within a \textbf{Debian} based distribution. Implemented a \textbf{FastAPI} service to proficiently generate recommendations and incorporated an additional layer for optimal web traffic management through an \textbf{NGINX} Server.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{nvim-conda} $|$ \emph{Lua, Neovim}}{\href{https://www.github.com/kmontocam/nvim-conda}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Creation of a Neovim plugin to switch \texttt{conda} environments inside the text editor}
\resumeItem{Ensure compatibility with multiple operating systems and shells by leveraging core utilities.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{aprecio.mx} $|$ \emph{TypeScript, MongoDB, AWS}}{\href{https://aprecio.mx}{\underline{Site}}}
\resumeItemListStart
\resumeItem{Led the migration of an enterprise's cloud infrastructure, reducing costs by utilizing self-managed services with AWS Lightsail and S3 buckets.}
\resumeItem{ Implemented containerization for the application using \textbf{Node.js} on an \textbf{Alpine} distribution, facilitating better version control and streamlined releases}
\resumeItem{Developed a backend using \textbf{Express.js} and \textbf{MongoDB} to provide essential utilities and support for the application.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards}
\resumeSubHeadingListStart
\resumeSubheading
{Hackaton Banorte}{May 2023}
{Banco Mercantil del Norte, S.A.}{Monterrey, MX}
\resumeItemListStart
\resumeItem{Delivered the winning project on the artificial intelligence challenge.}
\resumeItem{Developed a complete data product, using \textbf{LangChain}, OpenAI's GPT-3.5 API and a Telegram Bot. All combined with a UX/UI redesign to implement these tools on an existing platform.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Languages}{: Spanish , English } \\
	      \textbf{Programming Languages}{: Python, Rust, TypeScript, JavaScript, Lua} \\
	      \textbf{Databases}{: PostgreSQL, Apache Cassandra, Prometheus, MongoDB} \\
	      \textbf{Developer Tools}{: GNU Core Utils, Git, Docker, Bash} \\
	      }}
\end{itemize}
\end{document}
